\documentclass[UTF8]{article}
\usepackage{ctex}
\begin{document}
    \section*{2008 PartA}
    Dear Bob,
    \\
    I'm writing this letter to apologize for my carelessness.
    When I came back home from Canada,I unpacked my luggage.
    I found the music CD you had lent to me in it.The sense of
    guilt consumed me at the thought of the CD which is one of
    your favourites.\\
    I intend to order the same one for you from Amazon.com or
    send the CD back to you via express mail.Please let me know
    which solution you prefer as soon as possible.\\
    Though the life in Canada has become a thing of the past,
    our friendship will never fade away.\\
    Yours truly,\\
    Li Ming
    \\\\
    我写这封信是为我的粗心大意表示歉意。我从加拿大回到家，就打开了行李。
    在里面发现了你借给我的音乐CD。一想到这是你最喜欢的CD之一，我就感到十分
    愧疚。\\
    我想从亚马逊网站订购同样的CD给你，或者用快递把这张CD寄还给你。你更倾向于
    哪种解决方案，请尽快告诉我。\\
    尽管在加拿大的生活已成为过去，但我们的友谊永远不会褪色。
    \\\\
    Dear Bob,\\
    I'm writing this letter to experss a sincere apology for my carelessness.
    On arriving home from Canada,I unpacked the luggage where I found the music CD 
    you had lent to me.I'm consumed with the sense of guilt at the though of the CD 
    being one of your favouriter.\\
    Ordering the same one for you from Amazon.com or returning yous original one by experss mail,
    which solution will be better?Please inform me of the solution you prefer at your earliest convenience.\\
    A thing of the past though the life in Canada has become,our friendship will never fade away.\\
    Yours truly,\\
    Li Ming
    \section*{2008 Part B}
    As the picture depicts,two disabled men who leave their crutches
    behind and bind their crippled legs together,set off on a new journey.
    The caption "with one leg from you,and one leg from me,we can go wherever 
    we like" highlights the invaluable spirit of cooperation.\\
    A simple life philosophy lies behind it,"United,we stand;divided,we full."
    In other words,cooperation is the best policy in face of challenges.
    Take Tu Youyou for example.In cooperation with colleagues,Tu Youyou discovered 
    a novel thrapy against malaria.She won the Nobel Prize in Medicine for the remarkable 
    achievement.Likewise,Chinese government and its people together sailed through the 
    crisis of SARS in 2003.These examples indicate that things differ greatly with cooperation.
    It can generate collective achievements and ultimate success.\\
    The potential benefits of cooperation are clear.The resources,such as databases,
    strategies and social connection,could 
    be shared through cooperation,which can create more value and improve resource utilization.
    So cooperation must be rooted in us--in the lives we lead,the work we share,and even the 
    competitions the rivals participate in.\\
    \\
    图画中描绘的是，两个残疾人丢掉了他们的拐杖，将各自有残疾的腿绑在一起，开始一段新的旅程。
    “你一条腿，我一条腿；你我一起，走南闯北”的话语强调了一种异常珍贵的精神——合作。\\
    图画背后蕴含着一个简单的生活哲理:“合则立，分则败”。换句话说，合作是应对挑战的最佳策略。
    以屠呦呦的事迹为例。通过与同事的合作，屠呦呦发现了治疗疟疾的新型疗法，并凭借这项非凡成就获得了诺贝尔医学奖。
    同样的，2003年的非典危机也是在中国政府和全国人民的协作之下才顺利化解。这些事例表明，一旦我们开始合作，
    事情就会大不相同。合作使我们获得共同的成就，取得最终的成功。\\
    合作的潜在优势显而易见。数据库、策略和人脉等资源都可以通过合作实现共享，这样可以创造更多的价值并提高资源利用率。
    因此，合作必须根植于我们的内心——我们的生活，我们共同的工作，乃至于对手的竞争中。
    \\\\
    What the picture depicts is that two disabled men--with their crutches left behind and crippled 
    legs bound together--set off a new journey.At the bottom of the picture presents the caption 
    "with one leg from each of us,we can go wherever we like",highlighting the invaluable spirit of cooperation.\\
    Behind it lies a simple life philosophy,"United,we stand;divided,we fall",which means cooperation is the best policy 
    in face of challenges.A good case in point is Tu Youyou,a famous pharmacologist in China.
    Tu Youyou,in cooperation with colleagues,discovered a novel therapy against malaria,for which she won 
    the Nobel Prize in Medicine.Likewise,the crisis of SARS in 2003 wouldn't have been sailed through without 
    the cooperation of Chinese government and its people.What these examples indicate is that things differ greatly with 
    cooperation,which can generate collective achievements and ultimate success.\\
    Undoubtedly,the potential benefits of cooperation go without saying.The resources--databases,strategies and social connections--could be 
    shared though cooperation,thus creating more value and improving resource utilization.
    Therefore,cooperation must be rooted in us--in the lives we lead,the work 
    we share,and even the competitions the rivals participate in,just like the proverb goes,"No one can whistle a symphony.
    It takes a whole orchestra to play it"
    \\
    \\
    \section*{2008 翻译}
    He believes that this very difficulty may have had the compensation advantage of forcing him to think long and 
    intently about every sentence,and thus enabling him to detect errors in reasoning and in his own observations.\\
    \\
    他认为或许正因为(语言表达上的)这种困难，他不得不长时间专注地思考每个句子，从而使他能发现自己在推理和观察中的错误，结果
    这反而成为他的优点。\\
    \\

    He asserted,also,that his power to follow a long and purely abstract train of thought was very limited,for 
    which reason he lelt certain that he never could have succeeded with mathematics.\\
    \\
    他还坚持认为自己进行长时间纯抽象思考的能力十分有限，由此他认定自己在数学方面不可能会有所建树。\\
    \\

    On the other hand,he did not accept as well founded the charge made by some of his critics that,
    while he was a good observer,he had no power of reasoning.\\
    \\
    另一方面，一些批评家指责他虽然善于观察，却不具备推理能力，而他认为这种说法是缺乏依据的。\\
    \\

    He adds humbly that perhaps he was "superior to the common run of men in noticing things which easily 
    escape attention,and in observing them carefully."\\
    \\
    他又谦逊的说道，或许自己“在注意容易被忽略的事物并对其加以仔细观察方面优于常人”。\\
    \\

    Darwin was convinced that the loss of these tastes was not only a loss of happiness,
    but might possibly be injurious to the intellect,and more probably to the moral character.\\
    \\
    达尔文确信，失去这些爱好不只是缺少了乐趣，而且可能会有损思维能力，更有可能导致道德品质的下降。
    \section*{2021 Part A}
    Dear Friend,\\
    I'm happy to hear that you intent to find a job in China.
    I'd like to extend my warmest welcome to you.Hear are some suggestions 
    about how to stand out during the interviews and what to care about in the workplace.\\
    Firstly,you should learn about the cultural differences between China and your country in 
    advance,in case of some unnecessary misunderstandings both in the interviews and your later 
    career life.Moreover,remember to focus on and make full use of job-hunting websites and 
    applications in China.Last but not least,you need to prepare a resume in Chinese and 
    your related certificates.\\
    I hope that my suggestions are useful to you.Don't hesitate to contact me for more questions.\\
    Yours sincerely,\\
    Li Ming\\
    \\
    很开心得知你打算在中国找一份工作.我想向你表示热烈的欢迎.关于如何在面试中脱颖而出以及在职场中需要注意哪些
    事项,以下是我的一些建议.\\
    首先,你应该提前了解一下我们两国之间的文化差异,以防在面试和以后的职场生活中出现一些不必要的误解.
    另外,记得要关注并充分利用中国的招聘网站和招聘软件.最后但同样重要的是,你需要准备一份中文简历以及相关证书.\\
    希望我的建议对你有所帮助.如有其它问题,随时与我联系.\\
    \\
    Dear Friend,\\
    I'm very glad to hear that you intend to hunt for a job in China.I'd like to extend my warmest welcome 
    and also offer some suggestions about how to stand out during the interviews and what to care about in 
    the workplace.\\
    First and foremost,to avoid some unnecessary misunderstandings both in the interviews and your latter 
    career life,you are supposed to learn about the cultural diversity between our two nations in advance.
    What's more,more attention should be placed on various Chinese recruitment websites and applications--
    Zhaopin,51job as well as BOSS Zhipin,and you should take full advantage of them.Last but not least,you 
    need to prepare a Chinese resume as well as related certificates that can prove your personal ability.\\
    Hope the suggestions above will be more or less helpful to you.Please feel free to contact me if you 
    have any questions.\\
    Yours sincerely,\\
    Li Ming\\
    \section*{2021 Part B}
    As is vividly portrayed in the picture above,a boy who dresses up as "Sun Wukong" is complaining 
    that many of his classmates think studying Chinese opera performance is a little bit boring.
    However,his father is encouraging him to persevere in what he likes.\\
    The life philosophy that the picture conveys is that young people should not blindly follow 
    others' views,but bravely stick to their own interest.The story of ping-pong player Deng Yaping 
    can illustrate the theme of the picture well.When Deng Yaping first learned playing ping-pong,
    many people around her thought she was too short to play ping-pong.However,with the encouragement 
    of her father,she trained hard regardless of others' opinions and finally became the world champion.
    It turns out that persisting in the right choices,not other people's perspectives,plays an importtant 
    part in our future life.\\
    In my opinion,there is enormous external pressure in face of us,but we should adhere to our original 
    aspiration and follow our hearts.After all,you only live once,just do the things you like.\\
    \\
    正如上图生动描述的那样,一个装扮成"孙悟空"的男孩抱怨道,他的很多同学觉得学习中国戏曲表演有些无聊.然而,他的父亲
    鼓励他坚持做自己喜欢的事情.\\
    图画所传达的人生哲理是:年轻人不应该盲目听从他人的看法,而是要勇敢地坚持自己的兴趣.乒乓球运动员邓亚萍的故事
    能够很好地阐述图画的主题.邓亚萍在最初学习打乒乓球时,周围的人觉得她个子太矮,不能打乒乓球.然而,在爸爸的鼓励下,
    她不顾别人的看法,刻苦训练,最终成了世界冠军.事实证明,对我们未来生活起关键性作用的是对正确选择的坚持,而非他人的看法.\\
    在我看来,我们都会面对来自外界的巨大压力,但我们应该坚持初心,听从内心的声音.毕竟,人生只有一次,要去做自己喜欢的事.\\
    \\
    What is vividly portrayed in the above picture is such a scene:
    a boy who dresses up as "Sun Wukong",a role in Peking opera,is 
    complaining that many of his classmates think studying Chinese 
    opera performance is a little bit boring;while his father is 
    encouraging him to persevere in what he likes.\\
    As is conveyed in the picture,it is clear that young people,
    instead of blindly following others' views,should bravely stick 
    to their own interest.No better example can be used to illustrate the 
    theme of the picture than the story of ping-pong player Deng Yaping.
    Although many people around Deng Yaping thought she was too short 
    to play ping-pong from the very beginning,she,with the encouragement 
    of her father,trained hard regardless of others' opinions and finally 
    became the world champion.It turns out that it is not other people's 
    perspectives but persisting in the right choices of our own that plays 
    an important part in our future life.\\
    From my perspective,no matter how much pressure the outside world puts 
    on us,we should adhere to our original aspiration and follow our hearts.
    Just as Grandma Moses puts it,"Life is only once,do what you like."
    \section*{2021 翻译}
    Those societies came out of the war with levels of enrollment that 
    had been roughly constant at 3-5\% of the relevant age groups during 
    the decades before the war.\\
    \\
    二战后,西方社会适龄人群的入学率大致维持在3\%-5\%,与战前几十年间的
    水平相当.
    \\
    And the demand that rose in those societies for entry to higher 
    education extended to groups and social classes that had not 
    thought of attending a university before the war.\\
    \\
    在西方社会,人们对接受高等教育的需求上升,战前没有考虑上大学的群体
    和社会阶层也逐渐有了这样的需求.
    \\
    In many countries of Western Europe,the numbers of students in 
    higher education doubled within five-year periods during the 
    1960s and doubled again in seven,eight,or 10 year by the middle 
    of the 1970s.\\
    \\
    20世纪60年代,许多西欧国家接受高等教育的学生人数每5年翻一番,到70年代中期,
    这些人数在7,8年间或10年间又翻了一番.
    \\
    And when the new staff are predominantly young men and women fresh 
    from postgraduate study,they largely define the norms of academic 
    life in that faculty.\\
    \\
    且当新的员工大多是刚刚完成研究生学业的青年男女时,他们将在很大程度上
    界定该学院的学术生活规范.
    \\
    High growth rates increased the chances for academic innovation;
    they also weakened the forms and processes by which teachers and 
    students are admitted into a community of scholars during periods 
    of stability or slow growth.\\
    \\
    高增长率增加了学术创新的机会;同时也弱化了教师和学生在稳定期或缓慢增长期
    被接纳加入学者群体所需的形式和过程.
\end{document}